My title

### 2024-11-03 paper/paper.qmd
Update paper.qmd
Add packages citation to introduction

 【最后改结构描述加cross-reference】

>>>>

This project leverages several R packages, including tidyverse[@citeTidyverse], janitor[@citeJanitor], tidyr[@citeTidyr], dplyr[@citeDplyr], lubridate[@citeLubridate], arrow[@citeArrow], patchwork[@citePatchwork], car[@citeCar], kableExtra[@citeKableExtra], gridExtra[@citeGridExtra], moments[@citeMoments], grid[@citeGrid], rstanarm[@citeRstanarm], and testthat[@citeTestthat], to clean, organize, analyze, and visualize data in forecasting voter support for the 2024 U.S. presidential election. These packages support a reproducible and rigorous approach to data management, statistical modeling, and result presentation, ensuring transparency and accuracy throughout the analysis process.
 【最后改结构描述加cross-reference】
